A Gentle Introduction to Structural Causal Models

### 2021-05-20 presentation_video.Rmd
shorter

---
title: "A Gentle Introduction to Structural Causal Models"
author: "Daniel Saggau"
date: "5/11/2021"
output: beamer_presentation
citation_package: --biblatex
bibliography: [ref.bib]
---

@@

- Consists of system of equations 
- Assignment equation ':=' rather than regular equation '=' 
- Nonparametric SEM 
- Functional form rather than using  conditional probabilities
- entails features from the PO framework and graphical representation 
- Exogenous factors are part of the model specification

@@

Vanilla machine learning (ML), bayesian networks (BN) and regression models (Reg) are at the lowest level in the causal hierarchy (see table 1).
These methods demand the least information and depend on association alone.
Associational methods ignore external changes outside of our data.
The interventional distribution has information on these external changes.
The interventional distribution is only defined in high level causal methods.

>>>>

---
title: "A Gentle Introduction to Structural Causal Models"
author: "Daniel Saggau"
date: "5/11/2021"
citation_package: --biblatex
bibliography: [ref.bib]
output: 
  beamer_presentation:
    theme: Madrid

---

@@

- System of equations 
- Assignment equation ':=' rather than regular equation '=' 
- Nonparametric SEM 
- Functional form rather than using conditional probabilities
- SCM = PO + Graphical Tools

- Exogenous factors are part of the model specification

@@

 -ML, BN and regression are at the lowest level in the causal hierarchy
- Prediction methods demand the least information and depend on association alone
- Associational methods ignore external changes outside of our data.
- intervention distribution has information on these external changes.
- intervention distribution is only defined in high level causal methods.
